Automated Residual Plot Assessment with the R Package autovi and the Shiny App autovi.web

### 2024-11-26 autovi_paper.qmd
Some rephrasing.

In the context of regression model diagnostics, it describes the clarity of visual patterns on a diagnostic plot that may indicate model violations. This concept can be categorized as weak, moderate, or strong. However, in our study, we treat it as a continuous positive real variable. Importantly, its interpretation depends on how it is linked to a function of the data or the underlying data generating process. Consequently, the calculation of VSS can be vary across different model classes or within the same model, depending on the generating function.

>>>>

In the context of regression model diagnostics, VSS describes the clarity of visual patterns on a diagnostic plot that may indicate model violations. Violations can be categorized as weak, moderate, or strong, but here we treat it as a continuous positive real variable. Importantly, its interpretation depends on how it is linked to a function of the data or the underlying data generating process. Consequently, the calculation of VSS can be vary across different model classes or within the same model, depending on the generating function.
